Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-02-02 Multiresolution_framework/ltx/manuscript.tex
corrections at different places

\section{MRA of the IDE in State-Space}
The purpose of forming the multi-resolution approximation (MRA) of the integro-difference equation (IDE) is to form a multi-resolution finite-dimensional state-space model that best captures the spatiotemporal characteristics of the neural field. Given such a model, it is then possible to perform state and parameter estimation in an efficient and robust manner, thus allowing for subject-specific models.

The goal of this section is to demonstrate how to formulate a state-space model in a canonical form such that standard algorithms may be applied to estimate the multi-resolution connectivity structure. Therefore, the goal is to form a parameterized equation for coefficients of the field basis functions $\mathbf{x}_t$, which becomes the state vector.

@@

Now we will simplify the notation by defining vectors that contain all the translations of the wavelets and scaling functions 
\begin{align}      
	\boldsymbol\phi_{j_0}(r) \triangleq&\left\lbrace{\phi_{j_0,l}(r)}:l \in \mathbb{Z} \right\rbrace \\
	\boldsymbol\psi_{j}(r) \triangleq& \left\lbrace{\psi_{j,l}(r)}:l \in \mathbb{Z} \right\rbrace\\
	\boldsymbol\alpha_{j_0} \triangleq& \left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace \\
	\boldsymbol\beta_{j} \triangleq& \left\lbrace\beta_{j, l}:l \in \mathbb{Z} \right\rbrace \\
	\mathbf{x}_{t,j_0} \triangleq& \left\lbrace{x}_{t,j_{0},l}:l \in \mathbb{Z} \right\rbrace \\
	\check{\mathbf{x}}_{t,j} \triangleq& \left\lbrace{\check{x}}_{t,j,l}:l \in \mathbb{Z} \right\rbrace,
\end{align}
where $k = j_0,j$. Following this we can define the vectors 
\begin{align}
\boldsymbol\theta^\top \triangleq& [\begin{array}{ccccc} \boldsymbol\alpha_{j_0}^\top & \boldsymbol\beta_{j_0}^\top & \boldsymbol\beta_{j_0+1}^\top & \cdots & \boldsymbol\beta_{J}^\top \end{array}] 
\label{KernelWeights} \\
\mathbf{x}_{t}^\top \triangleq& [\begin{array}{ccccc}\mathbf{x}_{t,j_{0}}^\top &  \check{\mathbf{x}}_{t,j_{0}}^\top & \check{\mathbf{x}}_{t,j_{0}+1}^\top & \cdots & \check{\mathbf{x}}_{t,J}^\top\end{array}]
\label{FieldWeights} \\
\label{KernelBasisVector}
\boldsymbol\lambda^\top(r) \triangleq& \left[
\begin{array}{ccccc} \boldsymbol\phi_{j_0}^\top(r) &
\boldsymbol\psi_{j_0}^\top(r) & 
\boldsymbol\psi_{j_0+1}^\top(r) &
\cdots &
\boldsymbol\psi_{J}^\top(r)\end{array}\right] \\
\label{FieldBasisVector}
\boldsymbol\mu^\top (r) \triangleq& \left[
\begin{array}{ccccc}\boldsymbol\phi_{j_0}^\top(r) &
\boldsymbol\psi_{j_0}^\top(r) & 
\boldsymbol\psi_{j_0+1}^\top(r) &
\cdots &
\boldsymbol\psi_{J}^\top(r)\end{array}\right],
\end{align}
which allow us to write the neural field and connectivity kernel decomposition in the compact form of
\begin{align}
	w\left(r\right) &\approx \boldsymbol\theta^\top\boldsymbol\lambda\left(r\right) 
	\label{eq:KernelFiniteExpansion} \\
	v_t\left(r\right) &\approx \boldsymbol\mu^\top\left(r\right)\mathbf{x}_t.
	\label{eq:FieldFiniteExpansion}
\end{align}

@@

Now we have the compact for of the decomposition we can substitute this into the neural field equation \eqref{eq:DiscreteTimeModel} giving

@@

	 \mathbf{\Lambda}_{x} \triangleq \int_{\Omega}\boldsymbol{\mu}\left(r\right)\boldsymbol{\mu}^\top\left(r\right) \mathrm{d}r

@@

A very nice property of the MRAIDE framework is the the disturbance term becomes a vector valued, zero-mean normally distributed, white noise process 

@@

\parham{The state-transition equation can be simplified if the chosen family of wavelets are isotropic where}
\begin{equation}
	\boldsymbol{\lambda}_{j,l}(r-r') = \boldsymbol{\lambda}(2\mathbf{c}_{j,l}+r'-r). 
\end{equation}
Following this, we can switch the order of operations with the inner product and convolution in equation~\eqref{eq:ApproxDiscreteTimeModel4}. With this switch the convolution is now between the scaling functions and wavelets for the field and the scaling functions and wavelets for the connectivity kernel. This convolution can be calculated analytically when using B-spline wavelets and can be predefined once, since these are static functions. This has major computation advantages when solving the estimation problem. \parham{Although this switch holds theoretically it should be noted that it will introduce numerical error, specially close to the edges, due to the finite extent of the field. } The predefined convolution can be written as
\begin{equation}
	\left[\Gamma(r')\right]_{:j,l} = T_s \mathbf{\Lambda}_{x}^{-1}\int_{\Omega} \boldsymbol\mu\left(r\right)\boldsymbol\lambda\left(2c_{j,l} + r'-r\right) \,\mathrm{d}r
\end{equation}
giving
\begin{equation}
	\mathbf{x}_{t+1} = 
	\xi \mathbf{x}_t + 
	\int_{\Omega} \Gamma\left(r'\right)f\left(\boldsymbol\mu^\top\left(r'\right) \mathbf{x}_t\right) 
	\, \mathrm{d}r' \boldsymbol\theta
	+ \mathbf w_t
\end{equation}

@@

B-spline wavelet and scaling functions were formulated independently by \citet{Chui1992b,Chui1992,Unser1993}.  The scaling functions are $m$-th order B-splines and the compact support wavelet functions are a linear combination of scaling functions. B-spline wavelet and scaling functions approach optimal time/frequency localization as the order of the spline increases. In fact, for the cubic B-spline scaling and wavelet functions it is already close to the optimal limit for Gaussian functions and they have a better approximation rate than other wavelets with the same number of vanishing moments \citep{Unser1999}.

@@

The $m$-th  order cardinal B-spline function is defined by the recurrence relation \citep{Chui1992} 
\begin{equation}
N_{m}\left(r\right) = \left(N_{m-1}\ast N_{1}\right)\left(r\right) = \int_0^{1} N_{m-1}\left( r-r'\right)\,\mathrm{d}r',
\label{SplineConvolutionIntegral}
\end{equation}
where $m>1$, $\ast$ denotes convolution, and $N_1\left(r\right)$ is the characteristic function of the unit interval $\left[ 0,1\right)$, also known as indicator function, i.e.
\begin{equation}
N_{1}\left(r\right)=
\begin{cases}
1 & \text{if $ 0\le r<1$}, \\
0 & \mathrm{elsewhere}.
\end{cases}
\end{equation}
Following this, a B-spline of any order, $N_m(r)$, can be computed using the recursive expression defined by \citep{DeBoor2001}
\begin{equation}\label{eq:MRA-DoBoorFormula}
 N_{m}\left(r\right)=\frac{r}{m-1}N_{m-1}\left(r\right)+\frac{m-r}{m-1}N_{m-1}\left(r-1\right) \quad m>1.
 \end{equation}
The most commonly used form of splines is the cubic spline $\left(m=4\right)$, comprised of third degree polynomials added together at the joining points, with an explicit expression given by
\begin{align}
3!N_{4}\left(r\right)=
\begin{cases}
r^3 & \text{if $ 0\le r\le1$}, \\
4-12r+12r^2-3r^3 & \text{if $1\le r\le2$}, \\
-44+60r-24r^2+3r^3 & \text{if $2\le r\le3$}, \\
64-48r+12r^2-r^3 & \text{if $3\le r\le4$}, \\
0 & \mathrm{elsewhere}.
\end{cases}
\end{align}
One important feature of the B-spline functions is the \emph{partition of unity} property, meaning that the unity can be expressed as a linear sum of B-splines, i.e
\begin{equation}
	\sum_{l}N_m(r+l)\equiv1
	\end{equation}
	\parham{This is important as the underlying field can be reconstructed when its saturated without introducing numerical errors which is not the case for example in the case of Gaussian basis functions.}

The convolution and inner product of B-spline functions are required in order to formulate the multi-resolution framework described in the previous section (construction of $\boldsymbol\Lambda_{x}$, $\boldsymbol\Gamma$ and $\boldsymbol\Sigma_w$). To show how the convolution of two B-splines is calculated, \eqref{SplineConvolutionIntegral} can be rewritten as $(m-1)$ convolutions of the indicator function with itself
\begin{equation}\label{eq:N1convolutions}
 N_{m}\left(r\right)=\underbrace{\left(N_{1}\ast N_{1}\ast \cdots \ast N_{1}\right)}_{m-1\quad \text{convolutions}}\left(r\right).
\end{equation}
Using the associativity property of convolution, we have
\setlength{\arraycolsep}{0.0em}
\begin{align}\label{eq:BsplineConvolution}
N_{m}\left( r\right) \ast N_{m'}\left(r\right)&=\underbrace{\overbrace{\left(N_{1} \ast \cdots \ast N_{1}\right)}^{m-1 \quad \text{convolutions}}\left(r\right) \ast \overbrace{\left(N_{1} \ast \cdots \ast N_{1}\right)}^{m'-1\quad \text{convolutions}}}_{m+m'-1 \quad \text{convolutions}}\left(r\right)\nonumber\\
&=N_{m+m'}\left(r\right).
\end{align}
A direct consequence of \eqref{eq:BsplineConvolution} is the inner product between two B-splines is another translated B-spline such that
\begin{align}
 \left\langle N_{m}\left(r-l_{1}\right), N_{m'}\left(r-l_{2}\right)\right\rangle=&N_{m+m'}\left(m+l_{1}-l_{2}\right)\nonumber \\
=&N_{m+m'}\left(m'+l_{2}-l_{1}\right),
\label{eq:BsplineInnerProduct}
\end{align}
where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product. This holds as the support of $N_m\left(r\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$, i.e. $ N_{m}\left(\frac{m}{2}+r\right)=N_{m}\left(\frac{m}{2}-r\right)$ (see Appendix~\ref{ap:InnerProductOfBsplines} for explicit derivation). The values of $N_{m+m'}$ in \eqref{eq:BsplineInnerProduct} can be easily determined recursively by evaluating \eqref{eq:MRA-DoBoorFormula} at integer points, i.e.
 \begin{equation}\label{eq:MRA-recursiveBsplineatintegerpoints}
 \begin{cases}
 N_2(k)=\delta(k-1)\quad k\in \mathbb{Z}, \\
 N_{m}\left(k\right)=\frac{k}{m-1}N_{m-1}\left(k\right)+\frac{m-k}{m-1}N_{m-1}\left(k-1\right) \quad k=1,2,\dots,m-1
  \end{cases}
 \end{equation}
Note $N_{m}\left(k\right)=0$ for $k\le0$ or $k\ge m$.

@@

By exploiting \eqref{eq:BsplineConvolution} and \eqref{eq:BsplineInnerProduct}, the integrals in \eqref{eq:Lambdax}, \eqref{eq:Lambdatheta} and \eqref{eq:CovMatrix} can be computed analytically. In constructing $\boldsymbol\Lambda_{x}$, it is important to note that B-spline scaling and wavelet functions possess the following orthogonality properties \citep{Unser1993}: 
\begin{equation}
  \left\langle \varphi_{m;j_1,l_1}(r),\varphi_{m;j_2,l_2}(r)\right\rangle =0  \quad \mathrm{for} \quad j_1\neq j_2
 \label{eq:MRA-PsiPsiOrthogonality} 
 \end{equation}
 \begin{equation}
  \left\langle N_{m;j_1,l_1}(r),\varphi_{m;j_2,l_2}(r)\right\rangle =0  \quad \mathrm{for} \quad j_1\leq j_2.
 \label{eq:MRA-PhiPsiOrthogonality}
 \end{equation}
  \parham{Note from \eqref{eq:MRA-PsiPsiOrthogonality} B-spline wavelets are semi-orthogonal as they are not orthogonal with respect to translation on a given scale.}

>>>>

\section{MRA of the IDE in State-Space}
\parham{The purpose of} forming the multi-resolution approximation (MRA) of the integro-difference equation (IDE) is to form a multi-resolution finite-dimensional state-space model that best captures the spatiotemporal characteristics of the neural field. Given such a model, it is then possible to perform state and parameter estimation in an efficient and robust manner, thus allowing for subject-specific models.

\parham{The goal of this section is to demonstrate} how to formulate a state-space model in a canonical form such that standard algorithms may be applied to estimate the multi-resolution connectivity structure. \parham{Therefore, the goal is to form} a parameterized equation for coefficients of the field basis functions $\mathbf{x}_t$, which becomes the state vector.

@@

Now we will simplify the notation by defining vectors that contain all the translations of the wavelets and scaling functions 
\begin{align}      
	\boldsymbol\phi_{j_0}(r) \triangleq&\left\lbrace{\phi_{j_0,l}(r)}:l \in \mathbb{Z} \right\rbrace \\
	\boldsymbol\psi_{j}(r) \triangleq& \left\lbrace{\psi_{j,l}(r)}:l \in \mathbb{Z} \right\rbrace\\
	\boldsymbol\alpha_{j_0} \triangleq& \left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace \\
	\boldsymbol\beta_{j} \triangleq& \left\lbrace\beta_{j, l}:l \in \mathbb{Z} \right\rbrace \\
	\mathbf{x}_{t,j_0} \triangleq& \left\lbrace{x}_{t,j_{0},l}:l \in \mathbb{Z} \right\rbrace \\
	\check{\mathbf{x}}_{t,j} \triangleq& \left\lbrace{\check{x}}_{t,j,l}:l \in \mathbb{Z} \right\rbrace.
\end{align}
Following this we can define the vectors 
\begin{align}
\boldsymbol\theta^\top \triangleq& [\begin{array}{ccccc} \boldsymbol\alpha_{j_0}^\top & \boldsymbol\beta_{j_0}^\top & \boldsymbol\beta_{j_0+1}^\top & \cdots & \boldsymbol\beta_{J}^\top \end{array}] 
\label{KernelWeights} \\
\mathbf{x}_{t}^\top \triangleq& [\begin{array}{ccccc}\mathbf{x}_{t,j_{0}}^\top &  \check{\mathbf{x}}_{t,j_{0}}^\top & \check{\mathbf{x}}_{t,j_{0}+1}^\top & \cdots & \check{\mathbf{x}}_{t,J}^\top\end{array}]
\label{FieldWeights} \\
\label{KernelBasisVector}
\boldsymbol\lambda^\top(r) \triangleq& \left[
\begin{array}{ccccc} \boldsymbol\phi_{j_0}^\top(r) &
\boldsymbol\psi_{j_0}^\top(r) & 
\boldsymbol\psi_{j_0+1}^\top(r) &
\cdots &
\boldsymbol\psi_{J}^\top(r)\end{array}\right] \\
\label{FieldBasisVector}
\boldsymbol\mu^\top (r) \triangleq& \left[
\begin{array}{ccccc}\boldsymbol\phi_{j_0}^\top(r) &
\boldsymbol\psi_{j_0}^\top(r) & 
\boldsymbol\psi_{j_0+1}^\top(r) &
\cdots &
\boldsymbol\psi_{J}^\top(r)\end{array}\right],
\end{align}
which allow us to write the neural field and connectivity kernel decomposition in the compact form of
\begin{align}
	w\left(r\right) &\approx \boldsymbol\theta^\top\boldsymbol\lambda\left(r\right) 
	\label{eq:KernelFiniteExpansion} \\
	v_t\left(r\right) &\approx \boldsymbol\mu^\top\left(r\right)\mathbf{x}_t.
	\label{eq:FieldFiniteExpansion}
\end{align}

@@

Now we have the compact form of the decomposition we can substitute this into the neural field equation \eqref{eq:DiscreteTimeModel} giving

@@

	 \mathbf{\Lambda}_{x} \triangleq \int_{\Omega}\boldsymbol{\mu}\left(r\right)\boldsymbol{\mu}^\top\left(r\right) \mathrm{d}r,

@@

A very nice property of the MRAIDE framework is the disturbance term becomes a vector valued, zero-mean normally distributed, white noise process 

@@

\parham{The state-transition equation can be simplified if the chosen family of wavelets are isotropic where}
\begin{equation}
	\boldsymbol{\lambda}_{j,l}(r-r') = \boldsymbol{\lambda}(2\mathbf{c}_{j,l}+r'-r). 
\end{equation}
Following this, we can switch the order of operations with the inner product and convolution in equation~\eqref{eq:ApproxDiscreteTimeModel4}. With this switch the convolution is now between the scaling functions and wavelets for the field and the scaling functions and wavelets for the connectivity kernel. This convolution can be calculated analytically when using B-spline wavelets and can be predefined once, since these are static functions. This has major computation advantages when solving the estimation problem. \parham{Although this switch holds theoretically it should be noted that it will introduce numerical error, specially close to the edges, due to the finite extent of the field. } The predefined convolution can be written as
\begin{equation}\label{eq:Gammaij}
	\left[\Gamma(r')\right]_{:j,l} = T_s \mathbf{\Lambda}_{x}^{-1}\int_{\Omega} \boldsymbol\mu\left(r\right)\boldsymbol\lambda\left(2c_{j,l} + r'-r\right) \,\mathrm{d}r,
\end{equation}
giving
\begin{equation}
	\mathbf{x}_{t+1} = 
	\xi \mathbf{x}_t + 
	\int_{\Omega} \Gamma\left(r'\right)f\left(\boldsymbol\mu^\top\left(r'\right) \mathbf{x}_t\right) 
	\, \mathrm{d}r' \boldsymbol\theta
	+ \mathbf w_t.
\end{equation}

@@

B-spline wavelet and scaling functions were formulated independently by \citet{Chui1992b,Chui1992,Unser1993}.  The scaling functions are $m$-th order B-splines and the compact support wavelet functions are a linear combination of scaling functions. B-spline wavelet and scaling functions approach optimal time/frequency localization as the order of the spline increases. In fact, for the cubic B-spline scaling and wavelet functions it is already close to the optimal limit for Gaussian functions\citep{Unser1999}. 
%and they have a better approximation rate than other wavelets with the same number of vanishing moments

@@

The $m$-th  order cardinal B-spline function is defined by the recurrence relation \citep{Chui1992} 
\begin{equation}
N_{m}\left(r\right) = \left(N_{m-1}\ast N_{1}\right)\left(r\right) = \int_0^{1} N_{m-1}\left( r-r'\right)\,\mathrm{d}r',
\label{SplineConvolutionIntegral}
\end{equation}
where $m>1$, $\ast$ denotes convolution, and $N_1\left(r\right)$ is the characteristic function of the unit interval $\left[ 0,1\right)$, also known as indicator function, i.e.
\begin{equation}
N_{1}\left(r\right)=
\begin{cases}
1 & \text{if $ 0\le r<1$}, \\
0 & \mathrm{elsewhere}.
\end{cases}
\end{equation}
Following this, a B-spline of any order, $N_m(r)$, can be computed using the recursive expression defined by \citep{DeBoor2001}
\begin{equation}\label{eq:MRA-DoBoorFormula}
 N_{m}\left(r\right)=\frac{r}{m-1}N_{m-1}\left(r\right)+\frac{m-r}{m-1}N_{m-1}\left(r-1\right) \quad m>1.
 \end{equation}
The most commonly used form of splines is the cubic spline $\left(m=4\right)$, comprised of third degree polynomials added together at the joining points, with an explicit expression given by
\begin{align}
3!N_{4}\left(r\right)=
\begin{cases}
r^3 & \text{if $ 0\le r\le1$}, \\
4-12r+12r^2-3r^3 & \text{if $1\le r\le2$}, \\
-44+60r-24r^2+3r^3 & \text{if $2\le r\le3$}, \\
64-48r+12r^2-r^3 & \text{if $3\le r\le4$}, \\
0 & \mathrm{elsewhere}.
\end{cases}
\end{align}
One important feature of the B-spline functions is the \emph{partition of unity} property, meaning that the unity can be expressed as a linear sum of B-splines, i.e
\begin{equation}
	\sum_{l}N_m(r+l)\equiv1
	\end{equation}
	\parham{This is important as the underlying field can be reconstructed when its saturated without introducing numerical errors which is not the case for example when Gaussian basis functions are used.}

The convolution and inner product of B-spline functions are required in order to formulate the multi-resolution framework described in the previous section (construction of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Gamma$). To show how the convolution of two B-splines is calculated, \eqref{SplineConvolutionIntegral} can be rewritten as $(m-1)$ convolutions of the indicator function with itself
\begin{equation}\label{eq:N1convolutions}
 N_{m}\left(r\right)=\underbrace{\left(N_{1}\ast N_{1}\ast \cdots \ast N_{1}\right)}_{m-1\quad \text{convolutions}}\left(r\right).
\end{equation}
Using the associativity property of convolution, we have
\setlength{\arraycolsep}{0.0em}
\begin{align}\label{eq:BsplineConvolution}
N_{m}\left( r\right) \ast N_{m'}\left(r\right)&=\underbrace{\overbrace{\left(N_{1} \ast \cdots \ast N_{1}\right)}^{m-1 \quad \text{convolutions}}\left(r\right) \ast \overbrace{\left(N_{1} \ast \cdots \ast N_{1}\right)}^{m'-1\quad \text{convolutions}}}_{m+m'-1 \quad \text{convolutions}}\left(r\right)\nonumber\\
&=N_{m+m'}\left(r\right).
\end{align}
A direct consequence of \eqref{eq:BsplineConvolution} is the inner product between two B-splines is another translated B-spline such that
\begin{align}
 \left\langle N_{m}\left(r-l_{1}\right), N_{m'}\left(r-l_{2}\right)\right\rangle=&N_{m+m'}\left(m+l_{1}-l_{2}\right)\nonumber \\
=&N_{m+m'}\left(m'+l_{2}-l_{1}\right),
\label{eq:BsplineInnerProduct}
\end{align}
where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product. This holds as the support of $N_m\left(r\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$, i.e. $ N_{m}\left(\frac{m}{2}+r\right)=N_{m}\left(\frac{m}{2}-r\right)$ (see Appendix~\ref{ap:InnerProductOfBsplines} for explicit derivation). The values of $N_{m+m'}$ in \eqref{eq:BsplineInnerProduct} can be easily determined recursively by evaluating \eqref{eq:MRA-DoBoorFormula} at integer points, i.e.
 \begin{equation}\label{eq:MRA-recursiveBsplineatintegerpoints}
 \begin{cases}
 N_2(k)=\delta(k-1)\quad k\in \mathbb{Z}, \\
 N_{m}\left(k\right)=\frac{k}{m-1}N_{m-1}\left(k\right)+\frac{m-k}{m-1}N_{m-1}\left(k-1\right) \quad k=1,2,\dots,m-1
  \end{cases}
 \end{equation}
Note $N_{m}\left(k\right)=0$ for $k\le0$ or $k\ge m$.

@@

By exploiting \eqref{eq:BsplineConvolution} and \eqref{eq:BsplineInnerProduct}, the integrals in \eqref{eq:Lambdax} and \eqref{eq:Gammaij} can be computed analytically. In constructing $\boldsymbol\Lambda_{x}$, it is important to note that B-spline scaling and wavelet functions possess the following orthogonality properties \citep{Unser1993}: 
\begin{equation}
  \left\langle \varphi_{m;j_1,l_1}(r),\varphi_{m;j_2,l_2}(r)\right\rangle =0  \quad \mathrm{for} \quad j_1\neq j_2
 \label{eq:MRA-PsiPsiOrthogonality} 
 \end{equation}
 \begin{equation}
  \left\langle N_{m;j_1,l_1}(r),\varphi_{m;j_2,l_2}(r)\right\rangle =0  \quad \mathrm{for} \quad j_1\leq j_2.
 \label{eq:MRA-PhiPsiOrthogonality}
 \end{equation}
  \parham{Note from \eqref{eq:MRA-PsiPsiOrthogonality} B-spline wavelets are semi-orthogonal as they are not orthogonal with respect to translation on a given scale.}
